Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-01 article.qmd
Improve IDE figures

::: {#fig-constant layout-nrow=1}

::: {#fig-parameter layout-nrow=2 layout-valign="bottom"}
![](src/ide/constant.png)

![](src/ide/type_error.png)

`Constant` are assigned with `assign(..., constant=True)` and allow to link `Variable`s initial conditions,
while trying to use a `Parameter` instead is flagged as type errors (red underlining).
:::

::: {#fig-composition layout-nrow=1 layout-valign="bottom"}
![](src/ide/composition_tooltip.png)

A tooltip is shown when composing models,
which show the expected variables and their default values.
The IDE highlights mismatched types (`my_var` is `Variable` and `c` must be a number or a `Constant`)
and wrong names (`z` is not a name in `Model`).
:::

>>>>

::: {#fig-constant layout-nrow=1 layout-valign="bottom"}

::: {#fig-parameter}
![](src/ide/ide1.png)

`Constant` are assigned with `assign(..., constant=True)` and can be used to link `Variable`s initial conditions,
while trying to use a `Parameter` instead is flagged as type errors (red underlining).
The IDE automatically recognizes `e` as an `Equation`,
and provides autocompletion of the variables.
:::

::: {#fig-composition layout-nrow=1 layout-valign="bottom"}
![](src/ide/ide2.png)

A tooltip is shown when composing models,
which show the expected variables and their default values.
The IDE highlights
wrong names (`z` is not a name in `Model`)
and
mismatched types (`x` is `Variable` and `a` must be a number or a `Constant`)
:::
